### 2022-06-13 main/chapter_2ljets.tex
begin fleshing out low text

In Low regions, $\metsig \in 6\textrm{--}12$, $\zjets$ becomes a large
background contribution, since its fake $\met$, which arises from
from mismeasurements or rare interactions, is no longer eliminated.
Selections inherited from Intermediate regions to suppress
$\ttbar$ backgrounds also need supplementing.

Table~\ref{tab:2ljets_low}
Figure~\ref{fig:2ljets_low_minus}
Figure~\ref{fig:2ljets_low_region}
Figure~\ref{fig:2ljets_low2_region}
Figure~\ref{fig:2ljets_low_cr_region}
Figure~\ref{fig:2ljets_low_sr_or_cr_region}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_Rll_SRLow_noRll.pdf}
\caption{SR-Low$/\{\rll\}$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_mt2leplsp_0_SRLow_noRll_nomt2.pdf}
\caption{SR-Low$/\{\rll,\mttwoll\}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_absdPhiPllMet_SRLow2_noDphi.pdf}
\caption{SR-Low-2$/\{\dphillmet\}$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_absdPhiPllMet_SRLow2_noDphi_mg5.pdf}
\caption{SR-Low-2$/\{\dphillmet\}$, alternative}
\end{subfigure}
\caption[
Relaxed versions of SR-Low and SR-Low-2 to motivate their angular selections
]{%
Relaxed versions of SR-Low and SR-Low-2 to motivate their angular selections.
Each removes requirements listed in Table~\ref{tab:2ljets_low}:
(a) SR-Low removes $\rll$,
(b) SR-Low removes $\rll$ and $\mttwoll$,
and
(c, d) SR-Low-2 removes $\dphillmet$.
\\[0.5em]
Signals trend towards small $\rll$, plausibly due to their more boosted
$Z\rightarrow \ell^+\ell^-$ decays; small $\rll$ also suppresses $\ttbar$.
The mass of signals seen at small $\mttwoll$ in (b) motivates the design of
SR-Low-2.
Signals in SR-Low-2 spike at small $\dphillmet$ in (c); better statistical
precision is provided by an alternative $\zjets$ sample in (d).
}
\label{fig:2ljets_low_minus}
\end{figure}

>>>>

In Low regions, which have $\metsig \in 6\textrm{--}12$, the $\zjets$
background becomes a large since its fake $\met$, which arises from
from mismeasurements or rare interactions, is no longer eliminated.
Similarly, backgrounds from $\ttbar$ increase; the selections inherited from
Intermediate regions to suppress $\ttbar$ need supplementing.

Angular selections on lepton variables $\rll$ and $\dphillmet$ are used to
reject $\ttbar$ and provide signal sensitivity in Low regions, which are
defined in Table~\ref{tab:2ljets_low}.
Motivations for these angular selections are displayed in
Figure~\ref{fig:2ljets_low_minus}, and discussed here.

As elsewhere, binning of SR-Low in $\metsig \in 6\textrm{--}9\textrm{--}12$
increases sensitivity.
%TODO

Uniquely in Low regions and signal models of small mass splittings, it is
seen (from Figure~\ref{fig:2ljets_low_minus_norll_nomt2_mt2}) that some
substantial signal masses accumulate at small $\mttwoll$.
To capture these signals, SR-Low-2 is defined as the only
$\twoljets$-electroweak region with $\mttwoll < 80\,\eV[G]$.

That threshold of $80\,\eV[G]$ was chosen since after other selections for
SR-Low-2, almost all signal and background samples are in the spike near $0$;
a lower requirement would make little difference, and $80\,\eV[G]$ matches
other, usually inverted, selections.

The exclusion of $\metsig \in 9\textrm{--}12$ in SR-Low-2 is not particularly
well motivated.
This space contains about $2.3$ background expectation (mostly diboson) and
$\approx 1$ from some benchmark signals, so its inclusion as a single combined
bin not have increased sensitivity.
Its inclusion as an orthogonal bin with small yields would have added excessive
complication, however.

Figure~\ref{fig:2ljets_low_region}
Figure~\ref{fig:2ljets_low2_region}
Figure~\ref{fig:2ljets_low_cr_region}
Figure~\ref{fig:2ljets_low_sr_or_cr_region}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_Rll_SRLow_noRll.pdf}
\caption{SR-Low$/\{\rll\}$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_mt2leplsp_0_SRLow_noRll_nomt2.pdf}
\caption{SR-Low$/\{\rll,\mttwoll\}$}
\label{fig:2ljets_low_minus_norll_nomt2_mt2}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_absdPhiPllMet_SRLow2_noDphi.pdf}
\caption{SR-Low-2$/\{\dphillmet\}$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_absdPhiPllMet_SRLow2_noDphi_mg5.pdf}
\caption{SR-Low-2$/\{\dphillmet\}$, alternative}
\end{subfigure}
\caption[
Relaxed versions of SR-Low and SR-Low-2 to motivate their angular selections
]{%
Relaxed versions of SR-Low and SR-Low-2 to motivate their angular selections.
Each removes requirements listed in Table~\ref{tab:2ljets_low}:
(a) SR-Low removes $\rll$,
(b) SR-Low removes $\rll$ and $\mttwoll$,
and
(c, d) SR-Low-2 removes $\dphillmet$.
\\[0.5em]
Signals trend towards small $\rll$, plausibly due to their more boosted
$Z\rightarrow \ell^+\ell^-$ decays; small $\rll$ also suppresses $\ttbar$.
The mass of signals seen at small $\mttwoll$ in (b) motivates the design of
SR-Low-2.
Signals in SR-Low-2 spike at small $\dphillmet$ in (c); better statistical
precision is provided by an alternative $\zjets$ sample in (d).
}
\label{fig:2ljets_low_minus}
\end{figure}
